### 2016-01-19 paper.tex
Adjust wording per @nearyvs

Weighted averages for the transport terms in the mean kinetic energy
equation---analyzed identically to \cite{Bachant2015-JoT}---are shown in
Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding, we see
transport due to vertical advection at this point in the wake is approximately 3
times lower than the higher solidity UNH-RVAT. Note that direct comparison is
somewhat invalid, since the total measurement plane area is about 5\% lower for
this experiment. However, the differences observed are beyond this discrepancy.
We also see relatively lower levels of cross-stream turbulent transport due to
the lack of blade stall vortex shedding. These results may have interesting
implications regarding the application of turbines with lower power coefficient
to possibly improve overall array performance through enhanced transport of
kinetic energy from the free stream, though a detailed anaylsis of the
downstream evolution and turbine interaction will be necessary.

>>>>

Weighted averages for the transport terms in the mean kinetic energy
equation---analyzed identically to \cite{Bachant2015-JoT}---are shown in
Fig.~\ref{fig:Ktransport}. Due to the weaker blade vortex shedding, we see
transport due to vertical advection at this point in the wake is approximately 3
times lower than the higher solidity UNH-RVAT. Note that direct comparison is
somewhat invalid, since the total measurement plane area is about 5\% lower for
this experiment. However, the differences observed are beyond this discrepancy.
We also see relatively lower levels of cross-stream turbulent transport due to
the lack of blade stall vortex shedding. These results may have interesting
implications regarding the application of turbines with lower power coefficient
to possibly improve overall array performance through enhanced transport of
kinetic energy from the free stream, though evaluating these trade-offs will
require a detailed analysis of the downstream evolution and turbine--wake
interaction.
